Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-01-21 src-latex/parts/40-ocr-bench.tex
YES !

This section focuses on the evaluation of the performance of the three open-source OCR systems we selected, as described in \cref{sec:pipeline-summary}: Tesseract v4, Kraken and \peroocr.
The dataset used to perform this evaluation is composed of the $8,765$ entries (containing $424,764$ characters) from the dataset we previously introduced.
The single-column, cropped images of entries are used as input of each OCR system.
As the pages were previously deskewed, the text is mostly horizontal except for a few cases.
The expected output is the human transcription of these images provided in the dataset.
Before computing the Character Error Rate (CER) for each entry, each text prediction is normalized with the same basic rules as the ones used to post-process human transcription: dashes, quotes, and character codes for some glyphs like stars or hands are normalized.
% Regarding the charset of each OCR, Tesseract predicts characters covering a large portion of Latin script, \peroocr generates characters with a similar range, sometimes predicting some Cyrillic characters, and Kraken is constrained by its English model to predict only ASCII characters.

>>>>

This section focuses on the evaluation of the performance of the three open-source OCR systems we selected, as described in \cref{sec:pipeline-summary}: Tesseract v4, Kraken and \peroocr.
The dataset used to perform this evaluation is composed of the $8,765$ entries (containing $424,764$ characters) from the dataset we previously introduced.
The single-column, cropped images of entries are used as input of each OCR system.
As the pages were previously deskewed, the text is mostly horizontal except for a few cases.
The expected output is the human transcription of these images provided in the dataset.
Before computing the Character Error Rate (CER) for each entry, each text prediction is normalised with the same basic rules as the ones used to post-process human transcription: dashes, quotes and character codes for glyphs like stars or hands are normalised.
% Regarding the charset of each OCR, Tesseract predicts characters covering a large portion of Latin script, \peroocr generates characters with a similar range, sometimes predicting some Cyrillic characters, and Kraken is constrained by its English model to predict only ASCII characters.

### 2022-01-21 src-latex/parts/50-ner-xp1-training-set-size-and-pretraining.tex
YES !

\subsection{Training and evaluation protocol}
\label{sec:ner-xp1-protocol}
The following models form our baseline for both NER experiments.
Their short names written in square brackets will be used to reference them from now on.
\begin{itemize}
    \item \textbf{SpaCy NER pipeline for French~[SpaCy NER]}: We use the pipeline \textit{fr\_core\_news\_lg} provided by SpaCy v.3.2.1\mcite{spacy}, already trained for NER on the French corpora deep-sequoia and wikiner-fr.
    We stress again that we use the CNN version of this pipeline, not the transformer-based available in SpaCy v3.
    \item \textbf{Huggingface CamemBERT~[CmBERT]}: We rely on the implementation of BERT models provided by the software library Huggingface (transformers v.4.15.0, datasets v.1.17.0).
We chose to reuse a CamemBERT model published on the Huggingface repository \footnote{\url{https://huggingface.co/Jean-Baptiste/camembert-ner}} and already trained for NER on wikiner-fr.
\item \textbf{CamemBERT pre-trained on Paris directories~[CmBERT+ptrn]}: 
To evaluate whether adapting CamemBERT to the domain increases its performance, we do an unsupervised pre-training of CmBERT for next sentence prediction and masked language modeling, using approx. $845,000$ entries randomly sampled and OCRed with PERO.
The model is trained for 3 epochs and is available online\footnote{\url{https://huggingface.co/HueyNemud/das22-10-camembert_pretrained}}.
\end{itemize}

@@

\begin{figure}[ht!]
	   \center{\includegraphics[width=\textwidth]
	       {figs/eval-ner-exp1.pdf}}
	  \caption{\label{fig:f1-vs-trainsize} Metrics measured on the fine-tuned models CmBERT, CmBERT+ptrn and SpaCy NER for 8 training sets of increasing sizes. Precision and recall values are available in the appendix.}
\end{figure}

>>>>

\subsection{Training and evaluation protocol}
\label{sec:ner-xp1-protocol}
The following models form our baseline for both NER experiments.
Their short names written in square brackets will be used to reference them from now on.
\begin{itemize}
    \item \textbf{SpaCy NER pipeline for French~[SpaCy NER]}: We use the pipeline \textit{fr\_core\_news\_lg} provided by SpaCy v.3.2.1\mcite{spacy}, already trained for NER on the French corpora deep-sequoia and wikiner-fr.
    We stress again that we use the CNN version of this pipeline, not the transformer-based available in SpaCy v3.
    \item \textbf{Huggingface CamemBERT~[CmBERT]}: We rely on the implementation of BERT models provided by the software library Huggingface (transformers v.4.15.0, datasets v.1.17.0).
We chose to reuse a CamemBERT model published on the Huggingface repository \footnote{\url{https://huggingface.co/Jean-Baptiste/camembert-ner}} and trained for NER on wikiner-fr.
\item \textbf{CamemBERT pre-trained on Paris directories~[CmBERT+ptrn]}: 
To evaluate whether adapting CamemBERT to the domain increases its performance, we do an unsupervised pre-training of CmBERT for next sentence prediction and masked language modeling, using approx. $845,000$ entries randomly sampled and OCRed with PERO.
The model is trained for 3 epochs and is available online\footnote{\url{https://huggingface.co/HueyNemud/das22-10-camembert_pretrained}}.
\end{itemize}

@@

\begin{figure}[ht!]
	   \center{\includegraphics[width=\textwidth]
	       {figs/eval-ner-exp1.pdf}}
	  \caption{\label{fig:f1-vs-trainsize} Metrics measured on the fine-tuned models CmBERT, CmBERT+ptrn and SpaCy NER for 8 training sets of increasing sizes.}
\end{figure}

### 2022-01-21 src-latex/parts/80-conclusion.tex
YES !

% !TeX root = ../main-paper.tex
\section{Conclusion and future works}
We assessed the performance of three modern OCR systems on a set of historical sources of great interest in social history.
Although \peroocr clearly outperforms its competitors, the qualitative analysis of OCR errors shows that its failure cases are not the same as Tesseract.
This calls for leveraging both OCR systems in a complementary way to get the best of the two worlds.
%Moreover, we evaluate two deep-learning-based NER approaches in terms of their sensibility to the amount of training data and to noisy OCR texts.
The evaluation of SpaCy NER and CamemBERT (with and without pre-training) showed that BERT-based NER can benefit from pre-training and fine-tuning on a corpus produced with the same process than the texts to annotate.
%However, the results are not as good as for clean text: it is therefore interesting to investigate how to improve the OCR results or to correct the text in a postprocessing step.
Furthermore, it seems that all three models achieve good performance with relatively few training examples.
With a F1-score of 92\% with only 49 training examples, the pre-trained CamemBERT model seems to be a good choice to serve as a bootstrapping model to quickly produce large training sets and therefore lower the burden of creating a ground truth from scratch.
Besides, as directory entries always have the same structure - at least within a given index - we could take advantage of NER results and some simple rules to identify entries within pages instead of relying on the page layout only.
%, or, leveraging the low amount of training data required, interactively generate per-index NER models.
%Interesting points to discuss:
%\begin{itemize}
%    \item can we train on noisy data? (without manual OCR correction?) => future work? cf Pero OCR training procedure?
%    \item do we need better OCR systems or better post-correction techniques (if NER is reliable enough)?
%    \item Construction of the lexicon and associated cost \nathalie{là je ne comprends pas}
%\end{itemize}
%Ideas for future work:
%\begin{itemize}
%    \item Evaluate this: fine-tune Spacy NER on a few samples to generated a bootstrap dataset, feed it to BERT (cleaned or raw) to create an good model with minimal efforts ? \nathalie{les résultats de la table 2 ne plaident pas vraiment pour ça: même sur les très petits corpus, spacy est tours derrière...}
%    \item Use ML to infer regexes ?
%    \item As directories entries are always structured the same way (in a given list at least): use NER to identify entries within pages to save the burden of having to rely on the page layout ?
%\end{itemize}

>>>>

% !TeX root = ../main-paper.tex
\section{Conclusion and future works}
We assessed the performance of three modern OCR systems on a set of historical sources of great interest in social history.
Although \peroocr clearly outperforms its competitors, the qualitative analysis of OCR errors shows that its failure cases are not the same as Tesseract.
This calls for leveraging both OCR systems in a complementary way to get the best of the two worlds.
%Moreover, we evaluate two deep-learning-based NER approaches in terms of their sensibility to the amount of training data and to noisy OCR texts.
The evaluation of SpaCy NER and CamemBERT (with and without pre-training) showed that BERT-based NER can benefit from pre-training and fine-tuning on a corpus produced with the same process than the texts to annotate.
%However, the results are not as good as for clean text: it is therefore interesting to investigate how to improve the OCR results or to correct the text in a postprocessing step.
Furthermore, it seems that all three models achieve good performance with relatively few training examples.
With a F1-score of 92\% with only 49 training examples, the pre-trained CamemBERT model is a good choice to serve as a bootstrapping model to quickly produce large training sets and therefore lower the burden of creating a ground truth from scratch.
Besides, as directory entries always have the same structure - at least within a given index - we could take advantage of NER results and some simple rules to identify entries within pages instead of relying on the page layout only, or even interactively generate per-index NER models to take advantage of the low amount of training examples required.
%Interesting points to discuss:
%\begin{itemize}
%    \item can we train on noisy data? (without manual OCR correction?) => future work? cf Pero OCR training procedure?
%    \item do we need better OCR systems or better post-correction techniques (if NER is reliable enough)?
%    \item Construction of the lexicon and associated cost \nathalie{là je ne comprends pas}
%\end{itemize}
%Ideas for future work:
%\begin{itemize}
%    \item Evaluate this: fine-tune Spacy NER on a few samples to generated a bootstrap dataset, feed it to BERT (cleaned or raw) to create an good model with minimal efforts ? \nathalie{les résultats de la table 2 ne plaident pas vraiment pour ça: même sur les très petits corpus, spacy est tours derrière...}
%    \item Use ML to infer regexes ?
%    \item As directories entries are always structured the same way (in a given list at least): use NER to identify entries within pages to save the burden of having to rely on the page layout ?
%\end{itemize}
